Paper Figs

### 2023-02-14 graphs_newt_snakes/Paper_figs.Rmd
I am working out some of the figurse that should be on the paper

file$coevo_score <- ifelse(file$sim == "A" | file$sim == "B"| file$sim == "C" | file$sim == "D"| file$sim == "E"| file$sim == "I"| file$sim == "M", "False","True")
file$cor_score <- ifelse(file$sim == "A" | file$sim == "B"| file$sim == "C" | file$sim == "D"| file$sim == "E"| file$sim == "I"| file$sim == "M", "False","True")
file$exp = factor(file$exp, levels=c("No Interaction", "No Heritability", "Coevolution Flat Map"))

@@

@@

boxplot_coevo_slope_spec_avg(file1, file2, file3, title, subt, x_label, y_label)
```

>>>>

file$cor_score <- ifelse(file$sim == "A" | file$sim == "B"| file$sim == "C" | file$sim == "D"| file$sim == "E"| file$sim == "I"| file$sim == "M", "False","True")
file$exp = factor(file$exp, levels=c("No Interaction", "No Heritability", "Coevolution Flat Map"))

@@

boxplot_coevo_slope_spec_avg_advantage <- function(file1, file2, file3, title, subt, x_label, y_label){

newt_adv= c("D", "C", "B", "H", "G", "L")
mid= c("A", "F", "K", "P")
snake_adv = c("E", "I", "J", "M", "N", "O")

file$coevo_score = 0

file$coevo_score[file$sim %in% newt_adv] = "Newt Advantage"
file$coevo_score[file$sim %in% mid] = "No Advantage"
file$coevo_score[file$sim %in% snake_adv] = "Snake Advantage"
file$newt_snake_pheno_avg= (file$newt_pheno_change+file$snake_pheno_change)/2

  plot <-  ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_boxplot(aes(x=factor(sim, level=c("D", "C", "B", "H", "G", "L", "A", "F", "K", "P", "E", "I", "J", "M", "N", "O")), y=as.numeric(newt_snake_pheno_avg), fill=factor(coevo_score)))+

  theme(plot.title = element_text(size=5)) +
  #xlim(-1.1, 1.1)+
  facet_wrap(~exp, ncol=1)+
  scale_fill_manual(values =c("red", "purple", "blue"), labels=c('Newt Advantage', 'No Advantage', 'Snake Advantage'))+
    labs(fill = " ")+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      title =element_text(size=8, face='bold'))

@@

boxplot_coevo_slope_spec_avg(file1, file2, file3, title, subt, x_label, y_label)

boxplot_coevo_slope_spec_avg_advantage(file1, file2, file3, title, subt, x_label, y_label)
```
